Estimating Operator Intent\\ (Draft 4.0)

### 2015-10-01 intent.tex
more updates

\begin{enumerate}
\item
We recommend using a Bayesian {\bf (probabilistic) framework}
for intent recognition and prediction.
\item
We recommend developing an intent prediction system that can use
as {\bf many sensors and measurements} of the operator as possible.
\item
We seriously consider {\bf implanting devices and markers} in operators.
\item
We recommend each exoskeleton controller
to be used by and {\bf optimized for a single operator.}
A substantial investment in capturing the operator's normal behavior,
operator training and learning, and controller customization should be made.
\end{enumerate}

@@

Implanted electrodes
with wireless connections for signals and power
get high quality stable measurements.
For the class of users whose lives depend on the exoskeleton,
it might be worth implanting devices, if they did not interfere
with performance (soreness, pain in some positions or due to
movement). It is roughly equivalent to
operating with embedded shrapnel that has healed over.
A research goal would be getting these electrodes the size of rice
grains or smaller.

@@

These devices measure relative motion of tissue, and could be used
to measure force by measuring tendon stretch:\\
\url{http://bme.usc.edu/assets/004/54640.pdf}

@@

3) We seriously consider implanting devices and markers in operators.

@@

>>>>

\begin{enumerate}
\item
We recommend using a Bayesian {\bf (probabilistic) framework}
for intent recognition and prediction.
\item
We recommend developing an intent prediction system that can use
as {\bf many sensors and measurements} of the operator as possible.
\item
We recommend investigating recent developments in {\bf robot skin} to improve
operator-exoskeleton force estimation.
\item
We recommend each exoskeleton controller
to be used by and {\bf optimized for a single operator.}
A substantial investment in capturing the operator's normal behavior,
operator training and learning, and controller customization should be made.
\item
We recommend investigating {\bf implanting devices and markers} in operators.
For users whose lives depend on the exoskeleton,
it might be worth considering implanted devices.
\end{enumerate}

@@

Implanted electrodes
with wireless connections for signals and power
get high quality stable measurements.
For users whose lives depend on the exoskeleton,
it might be worth implanting devices, if they don't interfere
with performance (soreness, pain in some positions or due to
movement). It is roughly equivalent to
operating with embedded shrapnel that has healed over.
A research goal would be getting these electrodes the size of rice
grains or smaller.

@@

These implanted devices measure relative motion of tissue, and could be used
to measure force by measuring tendon stretch:\\
\url{http://bme.usc.edu/assets/004/54640.pdf}

\subsection{Robot Skin}

We recommend investigating recent developments in robot skin to improve
operator-exoskeleton force estimation (Figures~\ref{fig:softArtificialSkin}, \ref{fig:IonicLiquidSensors}, \ref{fig:fbgSkin}, and \ref{fig:waveguidesoftsensor}).\\
\url{http://softrobotics.cs.cmu.edu/research.html#SoftSkin}\\
\url{http://sml.me.cmu.edu/?page_id=38}\\
\url{http://softroboticstoolkit.com/book/egain-sensors}

\begin{figure}
\centering
\includegraphics[width=1\textwidth]{figs/softArtificialSkin.png}
\caption{Soft artificial skin sensors. (a) Multi-axis strain and pressure sensing skin. (b) Soft multi-axis force sensor.}
\label{fig:softArtificialSkin}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=1\textwidth]{figs/IonicLiquidSensors.png}
\caption{Ionic liquid microchannel embedded soft artificial skin sensors. (a) Soft strain sensor. (b) Hand motion detection artificial skin. (c) Soft pressure sensor using an EIT microchannel network.}
\label{fig:IonicLiquidSensors}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=1\textwidth]{figs/fbgSkin.png}
\caption{Fiber optically sensorized exoskeletal skin prototypes (a) FBG embedded skin structure with honeycomb patterns. (b) Human fingertip sized robotic finger with embedded FBGs.}
\label{fig:fbgSkin}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=1\textwidth]{figs/opticalsoftsensing.png}
\caption{Optical soft pressure sensor. (a) Preliminary prototype. (b) Prototype with light source and detector. (c) Stressed prototype showing cracked reflective coating. (d) Preliminary experimental result showing resistance increase in\
 the photo detector with increased curvature.}
\label{fig:waveguidesoftsensor}
\end{figure}

\subsection{Ultrasonic sensing}

Ultrasonic imaing is another way to estimate operator force.

Here is a blurb from a previous Atkeson proposal.
In the case of exoskeleton operators, we do not use a dry interface,
but can use well designed ultrasound transducers on the skin, probably
with a gel (vaseline-like) interface for good ultrasonic transmission.

We will explore using ultrasound transducers mounted in the skin
of the robot to see into the person being manipulated, to track bones,
tissue movement, and estimate tissue strain.
We can use real time ultrasound measurements
to locate bones to guide manipulation.
We can also use ultrasound to monitor tissue deformation (displacement and
strain) to guide forces and detect when a manipulation is failing and
should be stopped or adjusted.
Using phase-sensitive 2D speckle
tracking,
tissue deformation can be accurately
measured in real time at high spatial ($<$ 1 mm) and temporal ($<$ 10 ms)
resolution with a large imaging depth of a few cm at typical clinical
ultrasound imaging frequencies (2-10 MHz).
Based on the tissue displacement
information from speckle tracking, a complete set of “locally developed” strain
tensors of the deformed tissue will be generated, indicating the
degree of the strains of the tissue in different directions to guide
manipulation.
The ``globally applied''
strain also can be estimated by measuring the distance change of the
tissue and skin from the bones.
Non-linear analysis of ``locally
developed'' strain and ``globally applied'' strain will also
be applied to determine the criteria
at which tissue deforms significantly and passes into the
non-linear region of the soft tissue mechanics,
and the robot should change its behavior.
We will do feasibility tests using a
commercially available linear array transducer, connected to a
commercial ultrasound research platform (Verasonics US Engine, Verasonics Inc,
WA, USA), which will be mounted in the robot skin. A
set of off-the-shelf single element transducers will be mounted on the
palm and fingers of the robot hand for optimal sensing, imaging and
feedback. Based on the design parameters obtained, a custom
built array transducer system incorporated in the skin will be
developed and evaluated. We expect substantial revision and
improvements in our volumetric sensing in response to how well it does
in experimental use, including development of
better image processing algorithms, as we go.
In principle, the concept of mounting
ultrasound transducers in
robot skin is very similar to the
detection of prostate cancers from an ultrasound probe mounted
on a doctor's finger in the rectum to measure
the elastic properties of nearby tissue.
The integration of an ultrasound linear array
transducer onto the robot hand will also be similar to the approaches
of a previous study of muscle fatigue in the forearms.
Building a custom ultrasound transducer opens the possibility of distributing
the transducer across the skin, or putting
elements of the transducer in support surfaces such as a
bed or chair, and doing transmission
ultrasound imaging as well as reflective imaging. Transmission imaging
may give us better images at greater depth.

{\bf Preliminary Results:}
In previous work a commercial ultrasound
linear transducer integrated on to a simulated robot hand (knee pad)
measured local elasticity and contractility of the muscles in
the forearm. In the proposed
study, the knee pad will be replaced with an actual robot hand and the full
set of strain tensors will be calculated to determine the criteria for
pain and eventual tissue failure due to the applied shear force.
It should be noted that ultrasound may conduct poorly without a liquid
coupling and there is a potential challenge to image the tissues through
patient clothes. It was confirmed by our pilot tests that ultrasound
imaging is possible with a minimal spray of water (only enough to moisten
the clothes. A moisturizing device or sweat may be necessary
as part of the robot hand next to the ultrasound transducers.
We will also explore the use of other coupling materials such as very
soft silicone or gels,
which might allow ``dry'' measurements.

Initial tests also confirmed the feasibility of obtaining two
dimensional strain tensor fields from the ultrasound data obtained with
clothes on the forearm.
The strain tensor consists of the
axial, lateral and shear strains. The axial direction corresponds to
the direction of
propagation of ultrasound
while the lateral direction is
the one perpendicular to the axial direction.
If the measured strain goes beyond a specified threshold the robot would be
programmed to alter its manipulation procedure. Such real time strain
feedback comes with the possibility of reinforcement learning for the
robot.

@@

3) We recommend investigating recent developments in robot skin to improve
operator-exoskeleton force estimation.

@@

5) We recommend investigating implanting devices and markers in operators.
For users whose lives depend on the exoskeleton,
it might be worth considering implanted devices.
